Parameter precision in economic growth models inspired by Ecological Economics

### 2015-10-12 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Added first 2 sentences of Paper0.

>>>>

The book entitled
\emph{The Economic Growth Engine: How Energy and Work Drive Material Prosperity} 
\citep{Ayres:2010ug} 
was a watershed moment in the understanding 
of interactions between energy and the economy.
It represents the culmination of a decade of fruitful inquiry by Ayres and Warr, 
whose greatest insights
(that energy matters in economic growth,
that ``useful work'' dissipated at the point of production
is an essential factor of production, and
that the ``Cost Share Principle'' from neoclassical economics should be rejected)
were inspired by Ecological Economics in one way or another.
